Fast and Flexible Dynamic Binary Translation for the Kernel

### 2013-12-18 VEE-14/paper.tex
Added some comments about the trace allocator to the evaluation section.

\begin{figure*}[ht!]
\includegraphics[height=14em,clip=true,trim=0 -5em 10em -5em]{charts/lmbench_legend.eps}
\subfloat[Fast operations]{\epsfig{file=charts/lmbench_fast.eps,height=14em}}
\subfloat[Fork operations]{\epsfig{file=charts/lmbench_fork.eps,height=14em}}
\caption{\label{fig:lmbench}Microbenchmark results from \texttt{lmbench} that shows the effect of Granary's code cache optimizations (\Cref{sec:optimize}).}
\end{figure*}

@@

>>>>

\begin{figure*}
\includegraphics[height=14em,clip=true,trim=0 -5em 10em -5em]{charts/lmbench_legend.eps}
\subfloat[Fast operations]{\epsfig{file=charts/lmbench_fast.eps,height=14em}}
\subfloat[Fork operations]{\epsfig{file=charts/lmbench_fork.eps,height=14em}}
\caption{\label{fig:lmbench}Microbenchmark results from \texttt{lmbench} that shows the effect of Granary's code cache optimizations (\Cref{sec:optimize}).}
\end{figure*}

@@

The trace allocation optimization (\Cref{sec:trace_alloc}) does not result in significant performance improvements, and sometimes results in worse performance. This is because Granary's default allocation strategy (allocating space for instructions from per-CPU memory pools) already results in similar memory layouts to the trace allocator. A more significant difference would  be observed if Granary defaulted to a global allocation mechanism instead. Also, Granary's inclusion of function call instructions (\texttt{call}) into basic blocks likely works against the trace allocator. If basic blocks ended at \texttt{call} instructions, then the trace allocation strategy would arrange for the returning basic block and the returned-to basic blocks to be adjacent in memory.

%This is because the memory layout of basic blocks with and without the trace allocation optimization ends up being similar in Granary.
